---
title: "Appendix"
author: "Azure International"
date: "September 18, 2015"
output: html_document
---


```{r cache=T,echo=F,include=F}
# load in files once
# cache the data so we don't need to run it again
source("clean_functions_v2.R",verbose=F)
source("function_testbed.R",verbose=F)
source('graphing.R',verbose=F)
```

```{r,cache=T,echo=F,include=F}
# run this data every time we want a new model
source("function_testbed.R",verbose=F)

gm = 'zjk'
ssm = 'zjk'
tm = 'dem_scale'
ts= 1

get_grid_model(gridmodel = gm,
               special_subset_model = ssm,
               seasonal_hourly_load=seasonal_hourly_load,
               monthly_demand_profile=monthly_demand_profile,
               annual_demand=annual_demand,
               ccp_season=ccp_season,
               generation_forecast=generation_forecast,
               wind=wind,
               solar_month=solar_month,
               solar_day=solar_day,
               t_sched=t_sched,
               t_icap=t_icap,
               growth_cases,
               growth_case = 'noscale',
               demand_scale = 1,
               transmission_model = tm,
               transmission_scale = ts)

get_grid_model(gridmodel = gm,
               special_subset_model = ssm,
               seasonal_hourly_load=seasonal_hourly_load,
               monthly_demand_profile=monthly_demand_profile,
               annual_demand=annual_demand,
               ccp_season=ccp_season,
               generation_forecast=generation_forecast,
               wind=wind,
               solar_month=solar_month,
               solar_day=solar_day,
               t_sched=t_sched,
               t_icap=t_icap,
               growth_cases,
               growth_case = 'noscale',
               demand_scale = 1,
               transmission_model = tm,
               transmission_scale = ts)

```


```{r,cache=T,echo=F,include=F}
# # update this every time we want a NEW simulation

wsf = 0.9
sr = 1.08
etcr=0.5
rcc = 0.4
tp=24

run_model_v2(     peak_season = c(12,1,2,6,7,8),
                  start_year="2012",
                  end_year="2025",
                  wind_scale_factor=wsf,
                  solar_scale_factor=1,
                  time_period=tp,
                  wind_transmission_share = 0,
                  solar_transmission_share = 0,                  
                  extra_trans_capacity_renewables = etcr,   
                  gw_load_base_wind_ratio = 0,
                  gw_load_base_solar_ratio = 0,
                  max_option = 1,
                  spinning_reserve=sr,
                  r_ccp_coal = rcc,
                  r_ccp_ng = 0.9,
                  pmin_noccp_coal = 0.5,
                  pmin_ccp_coal = 0.85,
                  pmax_ccp_coal = 0.95,
                  pmin_noccp_ng = 0.3,
                  pmin_ccp_ng = 0.85,
                  pmax_ccp_ng = 0.95,
                  offset_wind_hours=0,
                  randomize_transmission =F,
                  transmission_sd =0.03)

annual_analysis <- analyze_data_annually_v2(test_profile=model_part4) 
monthly_analysis <- analyze_data_monthly_v2(test_profile=model_part4)
quarterly_analysis <- analyze_data_quarterly_v2(test_profile=model_part4)
hourly_analysis <- analyze_data_hourly_v2(test_profile=model_part4)




```



## Simulation: Zhangjiakou Baseline

###Parameters

- *Wind Scale Factor:* **0.9**   
- *Dispatch Period (hours):* **24**  
- *Ratio of outflow transmission capacity available for renewables:* **0.5**  
- *Spinning Reserve level(100% + reserve):* **1.08**  
- *Ratio of CHP coal to total coal:* **0.4**  
- *Wind Hourly Model Offset Hours:* **0**  
- *Base grid model:* **zjk**  
- *Special subset grid model:* **zjk**  
- *Transmission installed capacity model:* **dem_scale**  
- *Transmission line scale level:* **1**  



```{r,cache=T,echo=F,fig.align='center'}
library(ggplot2,verbose=F)
library(dplyr,verbose=F)
library(tidyr,verbose=F)
source('graphing.R',verbose=F)
library(gridExtra,verbose=F)
plot1(annual_analysis)
plot2(monthly_analysis)
plot3(hourly_analysis)
df <- plot4_pre_clean(model_part4)
plot4_aug(df)
plot4_oct(df)
plot4_dec(df)
plot5(model_part4,ye=2017,mo=1,days=4:10)
plot6(annual_analysis)
```












```{r,cache=T,echo=F,include=F}
# run this data every time we want a new model
source("function_testbed.R",verbose=F)

gm = 'zjk'
ssm = 'zjk'
tm = 'dem_scale'
ts= 0

get_grid_model(gridmodel = gm,
               special_subset_model = ssm,
               seasonal_hourly_load=seasonal_hourly_load,
               monthly_demand_profile=monthly_demand_profile,
               annual_demand=annual_demand,
               ccp_season=ccp_season,
               generation_forecast=generation_forecast,
               wind=wind,
               solar_month=solar_month,
               solar_day=solar_day,
               t_sched=t_sched,
               t_icap=t_icap,
               growth_cases,
               growth_case = 'noscale',
               demand_scale = 1,
               transmission_model = tm,
               transmission_scale = ts)

get_grid_model(gridmodel = gm,
               special_subset_model = ssm,
               seasonal_hourly_load=seasonal_hourly_load,
               monthly_demand_profile=monthly_demand_profile,
               annual_demand=annual_demand,
               ccp_season=ccp_season,
               generation_forecast=generation_forecast,
               wind=wind,
               solar_month=solar_month,
               solar_day=solar_day,
               t_sched=t_sched,
               t_icap=t_icap,
               growth_cases,
               growth_case = 'noscale',
               demand_scale = 1,
               transmission_model = tm,
               transmission_scale = ts)

```


```{r,cache=T,echo=F,include=F}
# # update this every time we want a NEW simulation

wsf = 0.9
sr = 1.08
etcr=0
rcc = 0.4
tp=24

run_model_v2(     peak_season = c(12,1,2,6,7,8),
                  start_year="2012",
                  end_year="2025",
                  wind_scale_factor=wsf,
                  solar_scale_factor=1,
                  time_period=tp,
                  wind_transmission_share = 0,
                  solar_transmission_share = 0,                  
                  extra_trans_capacity_renewables = etcr,   
                  gw_load_base_wind_ratio = 0,
                  gw_load_base_solar_ratio = 0,
                  max_option = 1,
                  spinning_reserve=sr,
                  r_ccp_coal = rcc,
                  r_ccp_ng = 0.9,
                  pmin_noccp_coal = 0.5,
                  pmin_ccp_coal = 0.85,
                  pmax_ccp_coal = 0.95,
                  pmin_noccp_ng = 0.3,
                  pmin_ccp_ng = 0.85,
                  pmax_ccp_ng = 0.95,
                  offset_wind_hours=0,
                  randomize_transmission =F,
                  transmission_sd =0.03)

annual_analysis <- analyze_data_annually_v2(test_profile=model_part4) 
monthly_analysis <- analyze_data_monthly_v2(test_profile=model_part4)
quarterly_analysis <- analyze_data_quarterly_v2(test_profile=model_part4)
hourly_analysis <- analyze_data_hourly_v2(test_profile=model_part4)




```



## Simulation: Zhangjiakou Island

###Parameters

- *Wind Scale Factor:* **0.9**   
- *Dispatch Period (hours):* **24**  
- *Ratio of outflow transmission capacity available for renewables:* **0**  
- *Spinning Reserve level(100% + reserve):* **1.08**  
- *Ratio of CHP coal to total coal:* **0.4**  
- *Wind Hourly Model Offset Hours:* **0**  
- *Base grid model:* **zjk**  
- *Special subset grid model:* **zjk**  
- *Transmission installed capacity model:* **dem_scale**  
- *Transmission line scale level:* **0**  



```{r,cache=T,echo=F,fig.align='center'}
library(ggplot2,verbose=F)
library(dplyr,verbose=F)
library(tidyr,verbose=F)
source('graphing.R',verbose=F)
library(gridExtra,verbose=F)
plot1(annual_analysis)
plot2(monthly_analysis)
plot3(hourly_analysis)
df <- plot4_pre_clean(model_part4)
plot4_aug(df)
plot4_oct(df)
plot4_dec(df)
plot5(model_part4,ye=2017,mo=1,days=4:10)
plot6(annual_analysis)
```















```{r,cache=T,echo=F,include=F}
# run this data every time we want a new model
source("function_testbed.R",verbose=F)

gm = 'zjk'
ssm = 'zjk_olympics'
tm = 'dem_scale'
ts= 1

get_grid_model(gridmodel = gm,
               special_subset_model = ssm,
               seasonal_hourly_load=seasonal_hourly_load,
               monthly_demand_profile=monthly_demand_profile,
               annual_demand=annual_demand,
               ccp_season=ccp_season,
               generation_forecast=generation_forecast,
               wind=wind,
               solar_month=solar_month,
               solar_day=solar_day,
               t_sched=t_sched,
               t_icap=t_icap,
               growth_cases,
               growth_case = 'noscale',
               demand_scale = 1,
               transmission_model = tm,
               transmission_scale = ts)

get_grid_model(gridmodel = gm,
               special_subset_model = ssm,
               seasonal_hourly_load=seasonal_hourly_load,
               monthly_demand_profile=monthly_demand_profile,
               annual_demand=annual_demand,
               ccp_season=ccp_season,
               generation_forecast=generation_forecast,
               wind=wind,
               solar_month=solar_month,
               solar_day=solar_day,
               t_sched=t_sched,
               t_icap=t_icap,
               growth_cases,
               growth_case = 'noscale',
               demand_scale = 1,
               transmission_model = tm,
               transmission_scale = ts)

```


```{r,cache=T,echo=F,include=F}
# # update this every time we want a NEW simulation

wsf = 0.9
sr = 1.08
etcr=0.5
rcc = 0.4
tp=24

run_model_v2(     peak_season = c(12,1,2,6,7,8),
                  start_year="2012",
                  end_year="2025",
                  wind_scale_factor=wsf,
                  solar_scale_factor=1,
                  time_period=tp,
                  wind_transmission_share = 0,
                  solar_transmission_share = 0,                  
                  extra_trans_capacity_renewables = etcr,   
                  gw_load_base_wind_ratio = 0,
                  gw_load_base_solar_ratio = 0,
                  max_option = 1,
                  spinning_reserve=sr,
                  r_ccp_coal = rcc,
                  r_ccp_ng = 0.9,
                  pmin_noccp_coal = 0.5,
                  pmin_ccp_coal = 0.85,
                  pmax_ccp_coal = 0.95,
                  pmin_noccp_ng = 0.3,
                  pmin_ccp_ng = 0.85,
                  pmax_ccp_ng = 0.95,
                  offset_wind_hours=0,
                  randomize_transmission =F,
                  transmission_sd =0.03)

annual_analysis <- analyze_data_annually_v2(test_profile=model_part4) 
monthly_analysis <- analyze_data_monthly_v2(test_profile=model_part4)
quarterly_analysis <- analyze_data_quarterly_v2(test_profile=model_part4)
hourly_analysis <- analyze_data_hourly_v2(test_profile=model_part4)




```



## Simulation: Zhangjiakou Olympics

###Parameters

- *Wind Scale Factor:* **0.9**   
- *Dispatch Period (hours):* **24**  
- *Ratio of outflow transmission capacity available for renewables:* **0.5**  
- *Spinning Reserve level(100% + reserve):* **1.08**  
- *Ratio of CHP coal to total coal:* **0.4**  
- *Wind Hourly Model Offset Hours:* **0**  
- *Base grid model:* **zjk**  
- *Special subset grid model:* **zjk_olympics**  
- *Transmission installed capacity model:* **dem_scale**  
- *Transmission line scale level:* **1**  



```{r,cache=T,echo=F,fig.align='center'}
library(ggplot2,verbose=F)
library(dplyr,verbose=F)
library(tidyr,verbose=F)
source('graphing.R',verbose=F)
library(gridExtra,verbose=F)
plot1(annual_analysis)
plot2(monthly_analysis)
plot3(hourly_analysis)
df <- plot4_pre_clean(model_part4)
plot4_aug(df)
plot4_oct(df)
plot4_dec(df)
plot5(model_part4,ye=2017,mo=1,days=4:10)
plot6(annual_analysis)
```













```{r,cache=T,echo=F,include=F}
# run this data every time we want a new model
source("function_testbed.R",verbose=F)

gm = 'jjt'
ssm = 'jjt'
tm = 'dem_scale'
ts= 1

get_grid_model(gridmodel = gm,
               special_subset_model = ssm,
               seasonal_hourly_load=seasonal_hourly_load,
               monthly_demand_profile=monthly_demand_profile,
               annual_demand=annual_demand,
               ccp_season=ccp_season,
               generation_forecast=generation_forecast,
               wind=wind,
               solar_month=solar_month,
               solar_day=solar_day,
               t_sched=t_sched,
               t_icap=t_icap,
               growth_cases,
               growth_case = 'noscale',
               demand_scale = 1,
               transmission_model = tm,
               transmission_scale = ts)

get_grid_model(gridmodel = gm,
               special_subset_model = ssm,
               seasonal_hourly_load=seasonal_hourly_load,
               monthly_demand_profile=monthly_demand_profile,
               annual_demand=annual_demand,
               ccp_season=ccp_season,
               generation_forecast=generation_forecast,
               wind=wind,
               solar_month=solar_month,
               solar_day=solar_day,
               t_sched=t_sched,
               t_icap=t_icap,
               growth_cases,
               growth_case = 'noscale',
               demand_scale = 1,
               transmission_model = tm,
               transmission_scale = ts)

```


```{r,cache=T,echo=F,include=F}
# # update this every time we want a NEW simulation

wsf = 0.9
sr = 1.08
etcr=0.2
rcc = 0.4
tp=24

run_model_v2(     peak_season = c(12,1,2,6,7,8),
                  start_year="2012",
                  end_year="2025",
                  wind_scale_factor=wsf,
                  solar_scale_factor=1,
                  time_period=tp,
                  wind_transmission_share = 0,
                  solar_transmission_share = 0,                  
                  extra_trans_capacity_renewables = etcr,   
                  gw_load_base_wind_ratio = 0,
                  gw_load_base_solar_ratio = 0,
                  max_option = 1,
                  spinning_reserve=sr,
                  r_ccp_coal = rcc,
                  r_ccp_ng = 0.9,
                  pmin_noccp_coal = 0.5,
                  pmin_ccp_coal = 0.85,
                  pmax_ccp_coal = 0.95,
                  pmin_noccp_ng = 0.3,
                  pmin_ccp_ng = 0.85,
                  pmax_ccp_ng = 0.95,
                  offset_wind_hours=0,
                  randomize_transmission =F,
                  transmission_sd =0.03)

annual_analysis <- analyze_data_annually_v2(test_profile=model_part4) 
monthly_analysis <- analyze_data_monthly_v2(test_profile=model_part4)
quarterly_analysis <- analyze_data_quarterly_v2(test_profile=model_part4)
hourly_analysis <- analyze_data_hourly_v2(test_profile=model_part4)




```



## Simulation: JJT Baseline

###Parameters

- *Wind Scale Factor:* **0.9**   
- *Dispatch Period (hours):* **24**  
- *Ratio of outflow transmission capacity available for renewables:* **0.2**  
- *Spinning Reserve level(100% + reserve):* **1.08**  
- *Ratio of CHP coal to total coal:* **0.4**  
- *Wind Hourly Model Offset Hours:* **0**  
- *Base grid model:* **jjt**  
- *Special subset grid model:* **jjt**  
- *Transmission installed capacity model:* **dem_scale**  
- *Transmission line scale level:* **1**  



```{r,cache=T,echo=F,fig.align='center'}
library(ggplot2,verbose=F)
library(dplyr,verbose=F)
library(tidyr,verbose=F)
source('graphing.R',verbose=F)
library(gridExtra,verbose=F)
plot1(annual_analysis)
plot2(monthly_analysis)
plot3(hourly_analysis)
df <- plot4_pre_clean(model_part4)
plot4_aug(df)
plot4_oct(df)
plot4_dec(df)
plot5(model_part4,ye=2017,mo=1,days=4:10)
plot6(annual_analysis)
```

















```{r,cache=T,echo=F,include=F}
# run this data every time we want a new model
source("function_testbed.R",verbose=F)

gm = 'jjt_olympics'
ssm = 'jjt'
tm = 'dem_scale'
ts= 1

get_grid_model(gridmodel = gm,
               special_subset_model = ssm,
               seasonal_hourly_load=seasonal_hourly_load,
               monthly_demand_profile=monthly_demand_profile,
               annual_demand=annual_demand,
               ccp_season=ccp_season,
               generation_forecast=generation_forecast,
               wind=wind,
               solar_month=solar_month,
               solar_day=solar_day,
               t_sched=t_sched,
               t_icap=t_icap,
               growth_cases,
               growth_case = 'noscale',
               demand_scale = 1,
               transmission_model = tm,
               transmission_scale = ts)

get_grid_model(gridmodel = gm,
               special_subset_model = ssm,
               seasonal_hourly_load=seasonal_hourly_load,
               monthly_demand_profile=monthly_demand_profile,
               annual_demand=annual_demand,
               ccp_season=ccp_season,
               generation_forecast=generation_forecast,
               wind=wind,
               solar_month=solar_month,
               solar_day=solar_day,
               t_sched=t_sched,
               t_icap=t_icap,
               growth_cases,
               growth_case = 'noscale',
               demand_scale = 1,
               transmission_model = tm,
               transmission_scale = ts)

```


```{r,cache=T,echo=F,include=F}
# # update this every time we want a NEW simulation

wsf = 0.9
sr = 1.08
etcr=0.2
rcc = 0.4
tp=24

run_model_v2(     peak_season = c(12,1,2,6,7,8),
                  start_year="2012",
                  end_year="2025",
                  wind_scale_factor=wsf,
                  solar_scale_factor=1,
                  time_period=tp,
                  wind_transmission_share = 0,
                  solar_transmission_share = 0,                  
                  extra_trans_capacity_renewables = etcr,   
                  gw_load_base_wind_ratio = 0,
                  gw_load_base_solar_ratio = 0,
                  max_option = 1,
                  spinning_reserve=sr,
                  r_ccp_coal = rcc,
                  r_ccp_ng = 0.9,
                  pmin_noccp_coal = 0.5,
                  pmin_ccp_coal = 0.85,
                  pmax_ccp_coal = 0.95,
                  pmin_noccp_ng = 0.3,
                  pmin_ccp_ng = 0.85,
                  pmax_ccp_ng = 0.95,
                  offset_wind_hours=0,
                  randomize_transmission =F,
                  transmission_sd =0.03)

annual_analysis <- analyze_data_annually_v2(test_profile=model_part4) 
monthly_analysis <- analyze_data_monthly_v2(test_profile=model_part4)
quarterly_analysis <- analyze_data_quarterly_v2(test_profile=model_part4)
hourly_analysis <- analyze_data_hourly_v2(test_profile=model_part4)




```



## Simulation: JJT Olmpics

###Parameters

- *Wind Scale Factor:* **0.9**   
- *Dispatch Period (hours):* **24**  
- *Ratio of outflow transmission capacity available for renewables:* **0.2**  
- *Spinning Reserve level(100% + reserve):* **1.08**  
- *Ratio of CHP coal to total coal:* **0.4**  
- *Wind Hourly Model Offset Hours:* **0**  
- *Base grid model:* **jjt_olympics**  
- *Special subset grid model:* **jjt**  
- *Transmission installed capacity model:* **dem_scale**  
- *Transmission line scale level:* **1**  



```{r,cache=T,echo=F,fig.align='center'}
library(ggplot2,verbose=F)
library(dplyr,verbose=F)
library(tidyr,verbose=F)
source('graphing.R',verbose=F)
library(gridExtra,verbose=F)
plot1(annual_analysis)
plot2(monthly_analysis)
plot3(hourly_analysis)
df <- plot4_pre_clean(model_part4)
plot4_aug(df)
plot4_oct(df)
plot4_dec(df)
plot5(model_part4,ye=2017,mo=1,days=4:10)
plot6(annual_analysis)
```


















```{r,cache=T,echo=F,include=F}
# run this data every time we want a new model
source("function_testbed.R",verbose=F)

gm = 'eimar'
ssm = 'eimar'
tm = 'hlbe_scale'
ts= 0.65

get_grid_model(gridmodel = gm,
               special_subset_model = ssm,
               seasonal_hourly_load=seasonal_hourly_load,
               monthly_demand_profile=monthly_demand_profile,
               annual_demand=annual_demand,
               ccp_season=ccp_season,
               generation_forecast=generation_forecast,
               wind=wind,
               solar_month=solar_month,
               solar_day=solar_day,
               t_sched=t_sched,
               t_icap=t_icap,
               growth_cases,
               growth_case = 'noscale',
               demand_scale = 1,
               transmission_model = tm,
               transmission_scale = ts)

get_grid_model(gridmodel = gm,
               special_subset_model = ssm,
               seasonal_hourly_load=seasonal_hourly_load,
               monthly_demand_profile=monthly_demand_profile,
               annual_demand=annual_demand,
               ccp_season=ccp_season,
               generation_forecast=generation_forecast,
               wind=wind,
               solar_month=solar_month,
               solar_day=solar_day,
               t_sched=t_sched,
               t_icap=t_icap,
               growth_cases,
               growth_case = 'noscale',
               demand_scale = 1,
               transmission_model = tm,
               transmission_scale = ts)

```


```{r,cache=T,echo=F,include=F}
# # update this every time we want a NEW simulation

wsf = 1.2
sr = 1.15
etcr=0
rcc = 0.23
tp=24

run_model_v2(     peak_season = c(12,1,2,6,7,8),
                  start_year="2012",
                  end_year="2025",
                  wind_scale_factor=wsf,
                  solar_scale_factor=1,
                  time_period=tp,
                  wind_transmission_share = 0,
                  solar_transmission_share = 0,                  
                  extra_trans_capacity_renewables = etcr,   
                  gw_load_base_wind_ratio = 0,
                  gw_load_base_solar_ratio = 0,
                  max_option = 1,
                  spinning_reserve=sr,
                  r_ccp_coal = rcc,
                  r_ccp_ng = 0.9,
                  pmin_noccp_coal = 0.5,
                  pmin_ccp_coal = 0.85,
                  pmax_ccp_coal = 0.95,
                  pmin_noccp_ng = 0.3,
                  pmin_ccp_ng = 0.85,
                  pmax_ccp_ng = 0.95,
                  offset_wind_hours=0,
                  randomize_transmission =F,
                  transmission_sd =0.03)

annual_analysis <- analyze_data_annually_v2(test_profile=model_part4) 
monthly_analysis <- analyze_data_monthly_v2(test_profile=model_part4)
quarterly_analysis <- analyze_data_quarterly_v2(test_profile=model_part4)
hourly_analysis <- analyze_data_hourly_v2(test_profile=model_part4)




```



## Simulation: EIMAR Baseline

###Parameters

- *Wind Scale Factor:* **1.2**   
- *Dispatch Period (hours):* **24**  
- *Ratio of outflow transmission capacity available for renewables:* **0**  
- *Spinning Reserve level(100% + reserve):* **1.15**  
- *Ratio of CHP coal to total coal:* **0.23**  
- *Wind Hourly Model Offset Hours:* **0**  
- *Base grid model:* **eimar**  
- *Special subset grid model:* **eimar**  
- *Transmission installed capacity model:* **hlbe_scale**  
- *Transmission line scale level:* **0.65**  



```{r,cache=T,echo=F,fig.align='center'}
library(ggplot2,verbose=F)
library(dplyr,verbose=F)
library(tidyr,verbose=F)
source('graphing.R',verbose=F)
library(gridExtra,verbose=F)
plot1(annual_analysis)
plot2(monthly_analysis)
plot3(hourly_analysis)
df <- plot4_pre_clean(model_part4)
plot4_aug(df)
plot4_oct(df)
plot4_dec(df)
plot5(model_part4,ye=2017,mo=1,days=4:10)
plot6(annual_analysis)
```

















```{r,cache=T,echo=F,include=F}
# run this data every time we want a new model
source("function_testbed.R",verbose=F)

gm = 'hlbe'
ssm = 'hlbe'
tm = 'hlbe_scale'
ts= 0.65

get_grid_model(gridmodel = gm,
               special_subset_model = ssm,
               seasonal_hourly_load=seasonal_hourly_load,
               monthly_demand_profile=monthly_demand_profile,
               annual_demand=annual_demand,
               ccp_season=ccp_season,
               generation_forecast=generation_forecast,
               wind=wind,
               solar_month=solar_month,
               solar_day=solar_day,
               t_sched=t_sched,
               t_icap=t_icap,
               growth_cases,
               growth_case = 'noscale',
               demand_scale = 1,
               transmission_model = tm,
               transmission_scale = ts)

get_grid_model(gridmodel = gm,
               special_subset_model = ssm,
               seasonal_hourly_load=seasonal_hourly_load,
               monthly_demand_profile=monthly_demand_profile,
               annual_demand=annual_demand,
               ccp_season=ccp_season,
               generation_forecast=generation_forecast,
               wind=wind,
               solar_month=solar_month,
               solar_day=solar_day,
               t_sched=t_sched,
               t_icap=t_icap,
               growth_cases,
               growth_case = 'noscale',
               demand_scale = 1,
               transmission_model = tm,
               transmission_scale = ts)

```


```{r,cache=T,echo=F,include=F}
# # update this every time we want a NEW simulation

wsf = 1.4
sr = 1.15
etcr=0
rcc = 0.18
tp=24

run_model_v2(     peak_season = c(12,1,2,6,7,8),
                  start_year="2012",
                  end_year="2025",
                  wind_scale_factor=wsf,
                  solar_scale_factor=1,
                  time_period=tp,
                  wind_transmission_share = 0,
                  solar_transmission_share = 0,                  
                  extra_trans_capacity_renewables = etcr,   
                  gw_load_base_wind_ratio = 0,
                  gw_load_base_solar_ratio = 0,
                  max_option = 1,
                  spinning_reserve=sr,
                  r_ccp_coal = rcc,
                  r_ccp_ng = 0.9,
                  pmin_noccp_coal = 0.5,
                  pmin_ccp_coal = 0.85,
                  pmax_ccp_coal = 0.95,
                  pmin_noccp_ng = 0.3,
                  pmin_ccp_ng = 0.85,
                  pmax_ccp_ng = 0.95,
                  offset_wind_hours=0,
                  randomize_transmission =F,
                  transmission_sd =0.03)

annual_analysis <- analyze_data_annually_v2(test_profile=model_part4) 
monthly_analysis <- analyze_data_monthly_v2(test_profile=model_part4)
quarterly_analysis <- analyze_data_quarterly_v2(test_profile=model_part4)
hourly_analysis <- analyze_data_hourly_v2(test_profile=model_part4)




```



## Simulation: HLBE Baseline

###Parameters

- *Wind Scale Factor:* **1.4**   
- *Dispatch Period (hours):* **24**  
- *Ratio of outflow transmission capacity available for renewables:* **0**  
- *Spinning Reserve level(100% + reserve):* **1.15**  
- *Ratio of CHP coal to total coal:* **0.18**  
- *Wind Hourly Model Offset Hours:* **0**  
- *Base grid model:* **hlbe**  
- *Special subset grid hlbe:* **hlbe**  
- *Transmission installed capacity model:* **hlbe_scale**  
- *Transmission line scale level:* **0.65**  



```{r,cache=T,echo=F,fig.align='center'}
library(ggplot2,verbose=F)
library(dplyr,verbose=F)
library(tidyr,verbose=F)
source('graphing.R',verbose=F)
library(gridExtra,verbose=F)
plot1(annual_analysis)
plot2(monthly_analysis)
plot3(hourly_analysis)
df <- plot4_pre_clean(model_part4)
plot4_aug(df)
plot4_oct(df)
plot4_dec(df)
plot5(model_part4,ye=2017,mo=1,days=4:10)
plot6(annual_analysis)
```


















```{r,cache=T,echo=F,include=F}
# run this data every time we want a new model
source("function_testbed.R",verbose=F)

gm = 'hle'
ssm = 'hle'
tm = 'hlbe_scale'
ts= 0.65

get_grid_model(gridmodel = gm,
               special_subset_model = ssm,
               seasonal_hourly_load=seasonal_hourly_load,
               monthly_demand_profile=monthly_demand_profile,
               annual_demand=annual_demand,
               ccp_season=ccp_season,
               generation_forecast=generation_forecast,
               wind=wind,
               solar_month=solar_month,
               solar_day=solar_day,
               t_sched=t_sched,
               t_icap=t_icap,
               growth_cases,
               growth_case = 'noscale',
               demand_scale = 1,
               transmission_model = tm,
               transmission_scale = ts)

get_grid_model(gridmodel = gm,
               special_subset_model = ssm,
               seasonal_hourly_load=seasonal_hourly_load,
               monthly_demand_profile=monthly_demand_profile,
               annual_demand=annual_demand,
               ccp_season=ccp_season,
               generation_forecast=generation_forecast,
               wind=wind,
               solar_month=solar_month,
               solar_day=solar_day,
               t_sched=t_sched,
               t_icap=t_icap,
               growth_cases,
               growth_case = 'noscale',
               demand_scale = 1,
               transmission_model = tm,
               transmission_scale = ts)

```


```{r,cache=T,echo=F,include=F}
# # update this every time we want a NEW simulation

wsf = 1.4
sr = 1.15
etcr=0
rcc = 1
tp=24

run_model_v2(     peak_season = c(12,1,2,6,7,8),
                  start_year="2012",
                  end_year="2025",
                  wind_scale_factor=wsf,
                  solar_scale_factor=1,
                  time_period=tp,
                  wind_transmission_share = 0,
                  solar_transmission_share = 0,                  
                  extra_trans_capacity_renewables = etcr,   
                  gw_load_base_wind_ratio = 0,
                  gw_load_base_solar_ratio = 0,
                  max_option = 1,
                  spinning_reserve=sr,
                  r_ccp_coal = rcc,
                  r_ccp_ng = 0.9,
                  pmin_noccp_coal = 0.5,
                  pmin_ccp_coal = 0.85,
                  pmax_ccp_coal = 0.95,
                  pmin_noccp_ng = 0.3,
                  pmin_ccp_ng = 0.85,
                  pmax_ccp_ng = 0.95,
                  offset_wind_hours=0,
                  randomize_transmission =F,
                  transmission_sd =0.03)

annual_analysis <- analyze_data_annually_v2(test_profile=model_part4) 
monthly_analysis <- analyze_data_monthly_v2(test_profile=model_part4)
quarterly_analysis <- analyze_data_quarterly_v2(test_profile=model_part4)
hourly_analysis <- analyze_data_hourly_v2(test_profile=model_part4)




```



## Simulation: HLE Baseline

###Parameters

- *Wind Scale Factor:* **1.4**   
- *Dispatch Period (hours):* **24**  
- *Ratio of outflow transmission capacity available for renewables:* **0**  
- *Spinning Reserve level(100% + reserve):* **1.15**  
- *Ratio of CHP coal to total coal:* **1**  
- *Wind Hourly Model Offset Hours:* **0**  
- *Base grid model:* **hle**  
- *Special subset grid hlbe:* **hle**  
- *Transmission installed capacity model:* **hlbe_scale**  
- *Transmission line scale level:* **0.65**  



```{r,cache=T,echo=F,fig.align='center'}
library(ggplot2,verbose=F)
library(dplyr,verbose=F)
library(tidyr,verbose=F)
source('graphing.R',verbose=F)
library(gridExtra,verbose=F)
plot1(annual_analysis)
plot2(monthly_analysis)
plot3(hourly_analysis)
df <- plot4_pre_clean(model_part4)
plot4_aug(df)
plot4_oct(df)
plot4_dec(df)
plot5(model_part4,ye=2017,mo=1,days=4:10)
plot6(annual_analysis)
```























```{r,cache=T,echo=F,include=F}
# run this data every time we want a new model
source("function_testbed.R",verbose=F)

gm = 'ym'
ssm = 'ym'
tm = 'hlbe_scale'
ts= 0.65

get_grid_model(gridmodel = gm,
               special_subset_model = ssm,
               seasonal_hourly_load=seasonal_hourly_load,
               monthly_demand_profile=monthly_demand_profile,
               annual_demand=annual_demand,
               ccp_season=ccp_season,
               generation_forecast=generation_forecast,
               wind=wind,
               solar_month=solar_month,
               solar_day=solar_day,
               t_sched=t_sched,
               t_icap=t_icap,
               growth_cases,
               growth_case = 'noscale',
               demand_scale = 1,
               transmission_model = tm,
               transmission_scale = ts)

get_grid_model(gridmodel = gm,
               special_subset_model = ssm,
               seasonal_hourly_load=seasonal_hourly_load,
               monthly_demand_profile=monthly_demand_profile,
               annual_demand=annual_demand,
               ccp_season=ccp_season,
               generation_forecast=generation_forecast,
               wind=wind,
               solar_month=solar_month,
               solar_day=solar_day,
               t_sched=t_sched,
               t_icap=t_icap,
               growth_cases,
               growth_case = 'noscale',
               demand_scale = 1,
               transmission_model = tm,
               transmission_scale = ts)

```


```{r,cache=T,echo=F,include=F}
# # update this every time we want a NEW simulation

wsf = 1.4
sr = 1.15
etcr=0
rcc = 0
tp=24

run_model_v2(     peak_season = c(12,1,2,6,7,8),
                  start_year="2012",
                  end_year="2025",
                  wind_scale_factor=wsf,
                  solar_scale_factor=1,
                  time_period=tp,
                  wind_transmission_share = 0,
                  solar_transmission_share = 0,                  
                  extra_trans_capacity_renewables = etcr,   
                  gw_load_base_wind_ratio = 0,
                  gw_load_base_solar_ratio = 0,
                  max_option = 1,
                  spinning_reserve=sr,
                  r_ccp_coal = rcc,
                  r_ccp_ng = 0.9,
                  pmin_noccp_coal = 0.5,
                  pmin_ccp_coal = 0.85,
                  pmax_ccp_coal = 0.95,
                  pmin_noccp_ng = 0.3,
                  pmin_ccp_ng = 0.85,
                  pmax_ccp_ng = 0.95,
                  offset_wind_hours=0,
                  randomize_transmission =F,
                  transmission_sd =0.03)

annual_analysis <- analyze_data_annually_v2(test_profile=model_part4) 
monthly_analysis <- analyze_data_monthly_v2(test_profile=model_part4)
quarterly_analysis <- analyze_data_quarterly_v2(test_profile=model_part4)
hourly_analysis <- analyze_data_hourly_v2(test_profile=model_part4)




```



## Simulation: YM Baseline

###Parameters

- *Wind Scale Factor:* **1.4**   
- *Dispatch Period (hours):* **24**  
- *Ratio of outflow transmission capacity available for renewables:* **0**  
- *Spinning Reserve level(100% + reserve):* **1.15**  
- *Ratio of CHP coal to total coal:* **0**  
- *Wind Hourly Model Offset Hours:* **0**  
- *Base grid model:* **ym**  
- *Special subset grid hlbe:* **ym**  
- *Transmission installed capacity model:* **hlbe_scale**  
- *Transmission line scale level:* **0.65**  



```{r,cache=T,echo=F,fig.align='center'}
library(ggplot2,verbose=F)
library(dplyr,verbose=F)
library(tidyr,verbose=F)
source('graphing.R',verbose=F)
library(gridExtra,verbose=F)
plot1(annual_analysis)
plot2(monthly_analysis)
plot3(hourly_analysis)
df <- plot4_pre_clean(model_part4)
plot4_aug(df)
plot4_oct(df)
plot4_dec(df)
plot5(model_part4,ye=2017,mo=1,days=4:10)
plot6(annual_analysis)
```








